Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
Distributed
We do not have OBRP definition

\medskip
\noindent
\textbf{Distributed implementation.}
While we have described the algorithm globally so far, we note that it allows for an efficient distributed implementations. 
The algorithm performs two types of operations that require communication with other clusters: a~component merge, and a~broadcast of the end of the phase.
We say that a~cluster containing $3$ isolated nodes is \emph{fresh}.
A merge of two components may require finding a~fresh cluster (for details see the proof of Lemma~\ref{lem:1req}).
In the following, we show how to efficiently find a~fresh cluster in a~distributed manner.
We organize the clusters into an arbitrary rooted balanced binary tree, and we broadcast the root to each cluster.
Each cluster maintains the counter of fresh clusters in its subtree.
To find a~fresh cluster, we traverse an arbitrary path of non-zero counters from the root.
Upon encountering a~fresh cluster, we end the traversal and decrease the counters on the followed path by $1$.
Summarizing, ending the phase requires a~single broadcast, and merging components has $O(\log \ell)$ communication complexity.

\subsection{Improved Algorithm for Online Rematching} \label{sec:k2}
In this section,
we present \RM,
 an algorithm for the \OBRP restricted to clusters of capacity $k=2$.
We interpret a~pair of nodes collocated in one cluster as a~``matched'' pair.
Hence,
the problem is an online variant of the maximal matching problem where
%a match is retractable.
%That is, 
a matched pair can separate in order to ``rematch'' with two other nodes.
Rematching is necessary for  maximizing intra-cluster communications,
which is dual to minimizing inter-cluster communications.
This is known as the  \emph{online rematching} 
problem and a~non-strict 7-competitive algorithm is already given by~\cite{repartition-disc},
in which the ratio comes with an additive factor in $O(\alpha\ell^2)$.
We do not only improve upon their competitive ratio,
but also show that our ratio holds \emph{strictly}
(i.e., with no additive factor).
Our algorithm is slightly simpler than the one in~\cite{repartition-disc}, 
while our analysis is significantly  simpler and more concise,
thanks to the charging scheme we devise here.

>>>>

\medskip
\noindent
\textbf{Distributed implementation.}
While we have described the algorithm globally so far, we note that it allows for an efficient distributed implementations. 
The algorithm performs two types of operations that require communication with other clusters: a~component merge, and a~broadcast of the end of the phase.
We say that a~cluster containing $3$ isolated nodes is \emph{fresh}.
A merge of two components may require finding a~fresh cluster (for details see the proof of Lemma~\ref{lem:1req}).
In the following, we show how to efficiently find a~fresh cluster in a~distributed manner.
To this end, we organize the clusters into an arbitrary rooted balanced binary tree, and we broadcast the root to each cluster.
Each cluster maintains the counter of fresh clusters in its subtree.
To find a~fresh cluster, we traverse an arbitrary path of non-zero counters from the root.
Upon encountering a~fresh cluster, we end the traversal and decrease the counters on the followed path by $1$.
Summarizing, ending the phase requires a~single broadcast, and merging components has $O(\log \ell)$ communication complexity.

\subsection{Improved Algorithm for Online Rematching} \label{sec:k2}
In this section,
we present \RM,
 an algorithm for clusters of capacity $k=2$.
We interpret a~pair of nodes collocated in one cluster as a~``matched'' pair.
Hence,
the problem is an online variant of the maximal matching problem where
%a match is retractable.
%That is, 
a matched pair can separate in order to ``rematch'' with two other nodes.
Rematching is necessary for  maximizing intra-cluster communications,
which is dual to minimizing inter-cluster communications.
This is known as the  \emph{online rematching} 
problem and a~non-strict 7-competitive algorithm is already given by~\cite{repartition-disc},
in which the ratio comes with an additive factor in $O(\alpha\ell^2)$.
We do not only improve upon their competitive ratio,
but also show that our ratio holds \emph{strictly}
(i.e., with no additive factor).
Our algorithm is slightly simpler than the one in~\cite{repartition-disc}, 
while our analysis is significantly  simpler and more concise,
thanks to the charging scheme we devise here.
